Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-27 writing/DraftExposurePaper/DraftExposurePaper.Rmd
edited frances wind dataset

```{r}
#Ike-2008 wind
#ike_wind <- read.csv("/Users/joshuaferreri/Documents/ike_wind.csv", na.strings = 999, header = TRUE)
#save(ike_wind, file = "writing/DraftExposurePaper/ike_wind.RData")
load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_wind.RData")
```

>>>>

```{r}
#Ike-2008 wind
#ike_wind <- read.csv("/Users/joshuaferreri/Documents/ike_wind.csv", na.strings = 999, header = TRUE)
#save(ike_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_wind.RData")
```

Frances wind data:

```{r}
frances_wind <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_wind.csv", na.strings = 999,
                         header = TRUE)
save(frances_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/frances_wind.RData")
```
